%!TEX encoding = UTF-8 Unicode
%!TEX spellcheck = English

\documentclass[a4paper,11pt,oneside]{amsart}
 

%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}

\usepackage{amsmath, latexsym, amsfonts, amssymb, amsthm, amscd}
%\usepackage{showkeys}
\usepackage{graphics,epsf,epsfig,psfrag}
\usepackage{perpage}
\usepackage{lastpage}
\usepackage{url}
\usepackage{color}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{hyperref}


\usepackage[itemsep=0.3em,topsep=0.3em,partosep=0em,parsep=0em,parskip=0em,leftmargin=2.2em,labelwidth=1.1em,labelsep=0.4em]{etaremune}

\renewcommand{\multicolsep}{0.1em}

\usepackage[a4paper,scale={0.75,0.75},marginratio={1:1}]{geometry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% FANCY PAGE LAYOUT %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{fancyhdr} 

\pagestyle{fancy}
%\fancyhead[R]{\sf Curriculum Vit\ae}
%\fancyhead[L]{\sf Francesco Caravenna}
\fancyhead[R]{}
\fancyhead[L]{}
\cfoot{\small \thepage\ / \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{8mm}


\fancypagestyle{plain}{% 
%\fancyhead{\sf ~} % empty header
\fancyhf{}
\cfoot{\small \thepage\ / \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{6.2mm}
}


\frenchspacing

\setlength{\parindent}{0pt}

%\usepackage[T1]{fontenc}
%%\usepackage[latin1]{inputenc} %under Linux
%\usepackage[ansinew]{inputenc} %under Windows


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% LIST ENVIRONMENTS %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newenvironment{myenumerate}{%
\renewcommand{\theenumi}{\arabic{enumi}}%
\renewcommand{\labelenumi}{{\rm(\theenumi)}}%
\begin{list}{\labelenumi}
	{%
	\setlength{\itemsep}{0.3em}%
	\setlength{\topsep}{0.3em}%
	\setlength{\partopsep}{0em}%
	\setlength{\parsep}{0em}%
	\setlength{\parskip}{0em}%
	\setlength\leftmargin{1.5em}%
	\setlength\labelwidth{1.1em}%
	\setlength{\labelsep}{0.4em}%
	\usecounter{enumi}%
	}%
	}%
{\end{list}
}

\renewenvironment{enumerate}{
\begin{myenumerate}}%
{\end{myenumerate}} 


\newenvironment{myitemize}{%
\begin{list}{$\bullet$}% 
 	{%
	\setlength{\itemsep}{0.3em}%
	\setlength{\topsep}{0.3em}%
	\setlength{\partopsep}{0em}%
	\setlength{\parsep}{0em}%
	\setlength{\parskip}{0em}%
	\setlength\leftmargin{1.5em}%
	\setlength\labelwidth{1.1em}%
	\setlength{\labelsep}{0.4em}%
%	\usecounter{enumi}%
	}%
	}%
{\end{list}}


\renewenvironment{itemize}{
\begin{myitemize}}%
{\end{myitemize}} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%% FOOTNOTES %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\MakePerPage[2]{footnote} % restarts footnote counter at every new page
\def\thefootnote{\fnsymbol{footnote}} % prints footnotes markers as symbols

%\long\def\symbolfootnote[#1]#2{\begingroup\def\thefootnote{\fnsymbol{footnote}}%
%\footnote[#1]{#2}\endgroup}
% for unnumbered footnotes, use \symbolfootnote[0]{text here}
% ... 1=*, 2=dagger, 3=doubledagger, etc.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\definecolor{myred}{RGB}{176,16,16}
\definecolor{myblack}{RGB}{0,0,0}

\titleformat{\section}{\color{myred}\titlerule[0.7pt]\color{myblack}}
{\color{myred}\rule[-0.4em]{0.7pt}{1.55em}\color{myblack}}
{.35em}{\bfseries\sffamily\MakeUppercase}

\titlespacing{\section}{0pt}{*3}{*1.5}
%\titlespacing{\section}{-0.35em}{*3}{*1.5}


%\newcommand{\mysection}[1]{%
%  \ifhmode\par\fi
%  \removelastskip
%  \vskip 0.7em
%  \begingroup
%  \textcolor{myred}{\noindent\rule[-0.5ex]{\columnwidth}{1.2pt}\nobreak}\par
%  \noindent
%  \vskip -0.15em\nobreak
%  \leavevmode\textcolor{myred}{\rule[-0.35em]{1.2pt}{1.55em}}%
%  \MakeUppercase{\hskip 0.8ex \bfseries \sffamily #1}\par
%  \vskip 0.5em\nobreak
%  \endgroup%
%%  \textcolor{myred}{\noindent\hrulefill\nobreak}
%  \nopagebreak%
%  }
%
%\renewcommand{\section}{\mysection}

\def\myskip{\vskip .175\baselineskip plus .175\baselineskip}
%\def\myskip{\smallskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{pxfonts} % Sets Palatino as main font
\renewcommand{\sfdefault}{iwona} % Sets Iwona as sans-serif font
%\usepackage[euler-digits]{eulervm} % Alternative math fonts (Euler)

\begin{document}
\LARGE
{\huge\sffamily\bfseries Francesco Caravenna}\hfill 
{\normalsize\sffamily \raisebox{0.53em}{[Last updated: \today]}}

{\sffamily Curriculum Vit\ae}

\vspace{1.5ex}

%\begin{center}
%{\sffamily\bfseries Curriculum Vit\ae\ of Francesco Caravenna}
%
%{\large\sffamily [Last updated: \today]}
%\end{center}

\normalsize

%\mbox{}

%\vfill

\section{Personal Details}

\begin{itemize}

\item Born on March 15, 1979, in Treviglio (BG), Italy.
%\\
%Married, two daughters (Marta 2014, Silvia 2017).

%\myskip

\item \emph{Office:} via Cozzi 55,\ 20125 Milano,\ Italy\\
\phantom{\emph{Office:}} office 3016, U5 building\\
\phantom{\emph{Office:}} phone +39 02 6448 5752

%\myskip

%\item \emph{Old working address:} via Trieste 63,\ 35121 Padova,\ Italy\\
%\emph{(still in use)}\phantom{\hskip 3.8em} office 539, ``Torre Archimede'' building\\
%\phantom{\emph{Old working address:}} phone +39 049 827 1472

%\myskip

\item \emph{E-mail:} \texttt{francesco.caravenna@unimib.it}

%\myskip

\item \emph{Home page:} \url{http://staff.matapp.unimib.it/~fcaraven/}

%\myskip

\item \emph{Language skills:} Italian (mother tongue), English, French

%\myskip

%\item \emph{Computer skills:} C, R, HTML/CSS, \LaTeX
\end{itemize}





\section{Education}

\begin{itemize}
\item
(2002 -- 2005)
\emph{Ph.D. in Mathematics}, University of Milano-Bicocca (I)
and University of Paris~7 (F). Advisors: Giambattista Giacomin,
Alberto Gandolfi.
%(Defense: 21 Oct 2005) 

\item
(1998 -- 2002) \emph{`Diploma di Licenza' in Physics} cum laude, %(mark: 70/70 e lode),
Scuola Normale Superiore of Pisa (I). Advisor: Sergio Caracciolo.
%(Defense: 19 Dec 2003)

\item
(1998 -- 2002) 
\emph{Master's Degree in Physics} cum laude, %(mark: 110/110 e lode),
University of Pisa (I). Advisor: Sergio Caracciolo.
%(Defenze: 23 Sep 2002)
\end{itemize}

\section{Academic Positions}

\begin{itemize}
\item (Oct 2016 -- present) \emph{Full Professor of Mathematics},
%(Probability and Statistics),
%Department of Mathematics and Applications, 
University of Milano-Bicocca (I).

\item (Nov 2010 -- Sep 2016) \emph{Associate Professor of Mathematics},
%(Probability and Statistics)},
%Department of Mathematics and Applications, 
University of Milano-Bicocca (I).

\item (Oct 2006 -- Oct 2010) \emph{Assistant Professor
of Mathematics}  (``Ricercatore'', tenured position),
%(Probability and Statistics)},
%Department of Pure and Applied Mathematics, 
University of Padova (I).

\item (Oct 2005 -- Sep 2006) \emph{Postdoc}
in the group of Erwin Bolthausen, 
%Institute of Mathematics,
University of Z\"urich (CH).
\end{itemize}

\section{Honors}

\begin{itemize}
\item Invited speaker at the \emph{International Congress of Mathematicians (ICM) 2026},
Philadelphia
%[joint section lecture with Rongfeng Sun and Nikos Zygouras]

\item Plenary speaker at \emph{4th Italian Meeting on
Probability and Mathematical Statistics}, Rome 2024

\item Winner of the ``Guido Fubini Prize 2011''
%(awarded by Istituto Superiore Mario Boella to a young mathematician based in Italy 
%working in the field of random processes)
\end{itemize}

\section{Editorial Services}

\begin{itemize}
\item Associate editor of
\textit{Annales de l'Institut Henri Poincar\'e} (2018 -- )

\item Associate editor of
\textit{Annals of Applied Probability} (2019 -- 2024)

%\item Referee for several journals, including
%\textit{Probability Theory and Related Fields}, 
%\textit{Annals of Probability},
%\textit{Communications in Mathematical Physics},
%\textit{Stochastic Processes and their Applications},
%\textit{Electronic Journal of Probability},
%\textit{Annales de l'Institut Henri Poincar\'e}, 
%\textit{Statistics and Probability Letters},
%\textit{Markov Processes and Related Fields},
%\textit{Potential Analysis}.

\end{itemize}

\section{Organization}

\begin{itemize}
\item C.I.M.E. Summer School \emph{``Statistical Mechanics and Stochastic PDEs''}
(Cetraro (CS), Italy, 11-15 September 2023)
[co-organised with Rongfeng Sun and Nikos Zygouras]

\item Workshop
\emph{``Self-interacting random walks, Polymers and Folding''}
(CIRM, Marseille (F), 9-13 September 2019)
[co-organised with Quentin Berger and Julien Poisat]

\item 
Third Workshop on \emph{``Large Scale Random Structures''}
(Milano-Bicocca, 10-11 July 2019)

\item Winter School
\emph{``Recent Breakthroughs in Singular Stochastic PDEs''}
(Milano-Bicocca, 2-6 February 2015)
%mini-courses by Massimiliano Gubinelli and Lorenzo Zambotti 
[co-organised with Federica Masiero and Gianmario Tessitore].

\item 
\emph{``XVIII Workshop on Quantitative Finance''} (Milano-Bicocca, January 25-26-27, 2017)
and
\emph{``XII Workshop on Quantitative Finance''} (Padova, January 27-28, 2011).
\end{itemize}

%\newpage
 




\section{Grants}

\begin{itemize}
\item Associated Investigator 
%for the Unit of Milano-Bicocca 
of the National Research Project
\emph{`Large Scale Random Structure'} (PRIN 2015) [PI: Fabio Martinelli]

\item Principal Investigator of the grant
\emph{`Probabilistic models for the statistical mechanics of polymers, 
interacting particle systems and applications'}
%(CPDA082105/08) 
of the University of Padova (2008)
%[founding: 34\,000 euros]

\item Member of National Research Projects (PRIN 2004, 2006, 2009) 
%in probability / statistical mechanics
\end{itemize}


\section{Ph.D. Students}

\begin{itemize}
\item (2023 -- present) Anna Donadini,
University of Milano-Bicocca and University of Pavia
(joint PhD with Indam).

\item (2019 -- 2023) Francesca Cottini,
University of Milano-Bicocca and University of Pavia
(joint PhD with Indam).
Thesis \emph{``Central limit theorems for polynomial chaos and fluctuations for 2d directed polymers''}
defended on 5 May 2023.


\item (2016 -- 2019) Giulia Comi,
University of Pavia and University of Milano-Bicocca
(joint PhD with Indam).
Thesis \emph{``Two fractional stochastic problems: semi-linear heat equation 
and singular Volterra equation''} defended on 13 December 2019.

\item (2012 -- 2015) Niccol\`o Torri,
University Claude Bernarde Lyon 1 (F) and University of Milano-Bicocca (I);
joint supervision with Fabio Lucio Toninelli.
Thesis \emph{``Localization and universality phenomena for
random polymers''} defended on 18 September 2015.


\item (2011 -- 2014) Jacopo Corbetta, University of Milano-Bicocca (I).
Thesis \emph{``General smile asymptotics and a multiscaling
stochastic volatility model''} defended on 4 March 2015.
\end{itemize}

%\newpage

\section{Research Interests}

My research activity is focused on \emph{probability theory and its applications}, including:
\begin{itemize}
\item Statistical Mechanics (disordered systems, random polymers)
\item Stochastic Equations (singular PDEs, scaling limits)
\item Random Walks (asymptotic properties, renewal theory)
%\item Mathematical Finance (stochastic volatility models, implied volatility)
\end{itemize}

%\smallskip
%{\hskip 1.2em}I have co-authored 24 papers published on top international journals,
%such as \emph{J. Eur. Math. Soc. (JEMS)}, 
%\emph{Probab. Theory Related Fields}, \emph{Ann. Probab.}, 
%\emph{Commun. Math. Phys.}, 
%\emph{Ann. Appl. Probab.}, 
%\emph{Stochastic Process. Appl.}, 
%\emph{Electron. J. Probab.}, 
%\emph{Ann. Inst. H. Poincar\'e}.
%

\newpage

\section{Publications}

\medskip
{\large\sf \bfseries Journal papers}
\smallskip

\begin{etaremune}
\input{../Publications/pub}
\end{etaremune}

\smallskip
\medskip
{\large\sf \bfseries Popular science}
\smallskip

\begin{itemize}
\item Q. Berger and F. Caravenna,
\textit{Simpson's paradox and anticovid vaccination data},
popular science article (2021) in Italian 
(\href{https://www.internazionale.it/notizie/quentin-berger/2021/12/09/vaccini-dati-paradosso-simpson}{Intenazionale.it}) 
and in French
(\href{https://theconversation.com/le-paradoxe-de-simpson-illustre-par-des-donnees-de-vaccination-contre-le-covid-19-170159}{The Conversation}).
\end{itemize}

\newpage

\smallskip
\medskip
{\large\sf \bfseries Proceedings}
\smallskip

\begin{itemize}
\input{../Publications/proc}
\end{itemize}

%\newpage

\smallskip
\medskip
{\large\sf \bfseries Textbook}
\smallskip

\begin{itemize}
\item Q. Berger, F. Caravenna, P. Dai Pra.
\textit{Probabilit\`a. Un'introduzione attraverso esempi, modelli e applicazioni.}
Seconda Edizione. Springer-Verlag Italia, Milano (2021).
\end{itemize}

%\newpage

%\textsf{BOOK}
%
%\begin{itemize}
%\item F. Caravenna, P. Dai Pra.
%\textit{Probabilit\`a. Un'introduzione attraverso modelli e applicazioni.}
%%UNITEXT - La matematica per il 3+2.
%Springer-Verlag Italia, Milano (2013).
%\end{itemize}
%
%\smallskip
%
%\newpage

\section{Research Visits}

\begin{itemize}
\item One/two weeks stay at 
\emph{Peking University / BICMR} (13-24 May 2024),
\emph{National University of Singapore} 
(8-19 May 2023, 18-29 Mar 2019, 27 Mar - 7 Apr 2017, 4-15 Apr 2016, 4-15 May 2015,
27 Jan - 8 Feb 2014, 14-25 May 2012), 
\emph{Durham University} (25-29 Sep 2023),
\emph{Univerist\'e Lyon 1} (13-16 May 2019),
\emph{University of Luxembourg} (13-17 Jun 2016),
\emph{University of Warwick} (16-21 Jun 2014),
\emph{University of Nantes} (18-22 Oct 2010),
\emph{Technical University of Berlin} (3-14 Nov 2008), \emph{ENS Lyon} (16-20 Jun 2008),
\textit{University of Paris 7} (17-21 Jul 2006, 19-23 May 2008),
\textit{University of Z\"urich} (28 Apr - 2 May 2008),
\emph{Technical University of Eindhoven} / \emph{Eurandom}
 (10-14 Jul 2006, 22-26 Oct 2007).

\item Five months at the \emph{Mathematical Institute} of the \emph{University of Leiden} (NL)
as a visiting professor in the framework of the
ERC Advanced Grant VARIS, at the invitation of Frank den Hollander
(17 March - 11 May 2012; 1 May - 30 June 2013; 1-30 March 2014) 

\item Two months at the
\textit{Laboratoire de Probabilit\'es et Mod\`eles Al\'eatoires},
\textit{Universities of Paris 6 and Paris 7} (F), at the invitation of Giambattista Giacomin
and Lorenzo Zambotti  (5 October - 13 December 2009) .

\item One month at the \emph{Institute of Mathematics} of the
\emph{Technical University of Berlin} (D)
at the invitation of Jean-Dominique Deuschel (8 January - 2 February 2007) .

%
%\item
%(16-21 Jun 2014)
%One week at the \emph{University of Warwick} (UK)
%at the invitation of Nikos Zygouras.
%
%\item
%(1-30 Mar 2014)
%One month at the \emph{University of Leiden} (NL)
%at the invitation of Frank den Hollander.
%
%\item
%(27 Jan - 8 Feb 2014)
%Two weeks at the \emph{National University of Singapore}
%at the invitation of Rongfeng Sun.
%
%\item
%(1 May - 30 Jun 2013)
%Two months at the \emph{University of Leiden} (NL)
%at the invitation of Frank den Hollander.
%
%\item
%(17 Mar - 11 May 2012)
%Two months at the \emph{University of Leiden} (NL)
%at the invitation of Frank den Hollander.
%
%\item
%(18-22 Oct 2010)
%One week at the \textit{University of Nantes} (F)
%at the invitation of Nicolas P\'etr\'elis.
%
%\item
%(5 Oct -- 13 Dec 2009)
%Two months at the 
%\emph{Laboratoire de Probabilit\'es et Mod\`eles Al\'eatoires},
%\emph{Universities of Paris 6 and Paris 7} (F), at the
%invitation of Giambattista Giacomin and Lorenzo Zambotti.
%
%\item
%(3-14 Nov 2008) Two weeks at the \emph{Technical University of Berlin} (D)
%at the invitation of Jean-Dominique Deuschel and Nicolas P\'etr\'elis.
%
%\item
%(16-20 Jun 2008) One week at \emph{ENS Lyon} (F) at the invitation of 
%Fabio Toninelli.
%
%\item
%(19-23 May 2008)
%One week at the \emph{University of
%Paris~7} (F) at the invitation of Giam\-bat\-ti\-sta Giacomin.
%
%\item
%(28 Apr - 2 May 2008)
%One week at the \emph{University of Z\"urich} (CH)
%at the invitation of Erwin Bolthausen and Nicolas P\'etr\'elis.
%
%\item
%(22-26 Oct 2007)
%One week at \emph{Eurandom} in
%Eindhoven (NL) at the invitation of Nicolas P\'etr\'elis.
%
%\item
%(5-9 Mar 2007; 23-27 Apr 2007)
%Two weeks at the \emph{University of
%Paris~7} (F) at the invitation of Giambattista Giacomin.
%
%\item
%(8 Jan - 2 Feb 2007) 
%One month at the \emph{Technical University of Berlin} (D)
%at the invitation of Jean-Dominique Deuschel.
%
%\item
%(17-21 Jul 2006)
%One week at the \emph{University of
%Paris~7} (F) at the invitation of Giambattista Giacomin.
%
%\item
%(10-14 Jul 2006)
%One week at \emph{Eurandom} in
%Eindhoven (NL) at the invitation of Nicolas P\'etr\'elis.
\end{itemize}




\section{Seminars}

%\smallskip
%I gave invited talks at national and international conferences,
%talks in universities and research centers, and didactic talks.

% EXTENDED
%{\hskip 1.2em}Ho tenuto per due volte (2007 e 2015) una conferenza breve 
%su invito al Congresso dell'Unione
%Matematica Italiana; sono stato \emph{plenary speaker}
%all'Italian Meeting on Hyperbolic Equations (2013);
%ho tenuto il Colloquium del Dipartimento di Matematica 
%all'Universit\`a di Leiden (2014).


%\newpage

%\smallskip
\medskip
{\large\sf \bfseries Invited Talks}
\smallskip


\begin{itemize}
\item (24 Jun 2025)
\emph{Noise sensitivity for the 2D Stochastic Heat Equation and directed polymers},
\emph{``Workshop on Irregular Stochastic Analysis''},
INdAM Meeting, Cortona (I).

\item (4 Apr 2025)
\emph{Noise Sensitivity and Critical 2D Directed Polymers},
Mark Kac Seminar, Utrecht (NL).

\item (6 Mar 2025)
\emph{The 2D Stochastic Heat Equation and related critical models},
Colloquium du LPSM (Laboratoire de Probabilités, Statistique et Modélisation),
Paris (F).

\item (11 Feb 2025)
\emph{Noise sensitivity for the 2D Stochastic Heat Equation},
\href{https://www.epfl.ch/labs/stoan/stoan/past-events/workshop-on-stochastic-equations-and-stochastic-dynamics/}{Workshop on ``Stochastic Equations and Stochastic Dynamics''},
SwissMap Research Station, Les Diablerets (CH).

\item (14 Jun 2024)
\emph{The 2d Stochastic Heat Equation and related critical models},
Plenary talk at the
\href{https://probabilityrome2024.it/plenary-speakers/}{4th Italian Meeting on
Probability and Mathematical Statistics},
Rome (I).

\item (23 Jan 2024)
\emph{Singolarità e Regolarità Aleatorie},
\href{https://www.unipr.it/node/104243}{Colloquium di Matematica, Fisica e Informatica},
University of Parma (I).

\item (23 Jan 2024)
\emph{Singolarità e Regolarità Aleatorie},
\href{https://www.unipr.it/node/104243}{Colloquium di Matematica, Fisica e Informatica},
University of Parma (I).

\item (11 Jan 2024)
\emph{Enhanced Schauder estimates for families of distributions},
Workshop \href{https://sites.google.com/view/spdesqft/home}{``Common trends and challenges in QFT and stochastic PDEs''},
University of Pavia (I).

\item (23 Dec 2023)
\emph{The critical $2d$ Stochastic Heat Frlow},
Workshop \href{https://warwick.ac.uk/fac/sci/statistics/news/criticality_workshop}{``Critical phenomena 
in statistical physics, continuum theories and SPDEs ''},
University of Warwick (UK).

\item (23 Oct 2023)
\emph{The critical $2d$ Stochastic Heat Frlow},
21st Symposium \href{https://sites.google.com/view/workshop-salsis/home/2023}{``Stochastic 
Analysis on Large Scale Interacting Systems''},
RIMS, Kyoto University (JP).

\item (1 Jun 2023)
\emph{Renewal Theory, Disordered Systems, and Stochastic PDEs},
Workshop \href{https://www.lebesgue.fr/en/polywalks/programme}{``Polymers and self-avoiding walks''}, 
University of Nantes (F).

\item (28 Mar 2023)
\emph{The critical $2d$ Stochastic Heat Frlow},
\href{https://personalpages.manchester.ac.uk/staff/xiong.jin/easter23/index.html}{UK Easter 
Probability Meeting},
University of Manchester (UK).

\item (26 Jan 2023)
\emph{Singolarità e Regolarità Aleatorie},
\href{https://umi.dm.unibo.it/milano26gennaio23/}{``I Seminari del Centenario''}, 
Cento anni di UMI 1922-2022, 
 University of Milano-Bicocca.

\item (9 Jan 2023)
\emph{On the 2d Stochastic Heat Equation and delta Bose gas},
Workshop \href{https://sites.google.com/view/mqm-workshop-2023/}{``Mathematical Quantum Matter''},
University of Milano (I).

\item (23 Sep 2022)
\emph{Renewal Theory, Disordered Systems, and Stochastic PDEs},
Workshop \href{https://sites.google.com/view/pdp60laquila/}{``A journey through complex systems''}
in honor of Paolo Dai Pra 60th birthday, L'Aquila (I).

\item (12 Sep 2022)
\emph{The critical 2d Stochastic Heat Flow},
Workshop  \href{https://www.mfo.de/occasion/2237/www_view}{``Large Scale Stochastic Dynamics''},
Mathematisches Forschungsinstitut Oberwolfach (D).

\item (26 Jul 2022)
\emph{Renewal Theory, Disordered Systems, and Stochastic PDEs},
Workshop 
\href{https://personalpages.manchester.ac.uk/staff/denis.denisov/LevyRW-workshop/index.html}{``Lévy 
Processes and Random Walks''}
in celebration of Ron Doney's 80th birthday,
Manchester (UK) [online talk].

\item (28 Jun 2022)
\emph{The critical 2d Stochastic Heat Flow},
SPA 2022 Conference, Invited session 
\href{https://spa2022.whu.edu.cn/Programme/Invited_sessions.htm}{``Stochastic 
Partial Differential Equations''},
Wuhan (CN) [online talk].

\item (2 May 2022)
\emph{The critical 2d Stochastic Heat Flow is not a Gaussian Multiplicative Chaos},
Workshop \href{https://conferences.cirm-math.fr/2799.html}{``Random Walk, 
Reinforcement and Localization''},
CIRM, Marseille (F).

\item (8 Sep 2021)
\emph{Gaussian Limits for Subcritical Chaos},
workshop \href{https://conferences.cirm-math.fr/2124.html}{``Directed Polymers and Folding''}, 
CIRM, Marseille (F).

\item (7 Jun 2021)
\emph{Central Limit Theorems in Disordered Systems and Stochastic PDEs},
\href{http://www.umi-prisma.polito.it/webinars.html}{UMI-PRISMA Seminar} [online talk].

\item (21 Jan 2021)
\emph{Hairer's Reconstruction Theorem without Regularity Structures},
\href{https://www.owprobability.org/one-world-probability-seminar/past-seminars#h.fejiyznu0y15}{One 
World Probability Seminar} [online talk].

\item (11 Sep 2020)
\emph{The two-dimensional directed polymer 
and the Dickman subordinator},
workshop \href{https://perso.math.u-pem.fr/asselah.amine/PORQ2020.html}{``Random Polymers 
and Networks''}, IGESA center, Porquerolles island (F).

\item (12 Nov 2019)
\emph{On the two-dimensional KPZ equation},
Conference of the Euro-Maghreb 
International Research Network in Mathematics and Applications,
Madrid (E).

\item (30 Oct 2019)
\emph{On the 2d KPZ Equation},
Half day in Stochastic Analysis and applications,
University of Padova (I).

\item (24 Oct 2019)
\emph{On the 2d KPZ and Stochastic Heat Equation},
Workshop on ``Singular SPDEs and Related Topics'',
Hausdorff Research Institute for Mathematics, Bonn (D).

\item (27 Sep 2019)
\emph{On the 2d KPZ and Stochastic Heat Equation},
Meeting of the AAP Editorial Board,
University of Nice (F).

\item (20 Jun 2019)
\emph{On the 2d KPZ and Stochastic Heat Equation},
Second Italian Meeting on Probability and Mathematical Statistics,
Vietri sul Mare (I).

\item (3 July 2018)
\emph{Moment asymptotics for 2d directed polymer and stochastic heat equation in the critical window},
Two days workshop on ``Large scale random structures'',
University of Padova (I).

\item (3 Apr 2018)
\emph{Moment asymptotics for 2d directed polymer and stochastic 
heat equation in the critical window},
Workshop ``Polymer, Folding and Phase Transition'', CIRM, Marseille (F).

\item (23 Jan 2018)
\emph{Pinning model, universality and rough paths},
Conference ``Universality and scaling limits of interacting random systems'',
Inhomogeneous Random Systems 2018, Institut H. Poincar\'e, Paris (F).

\item (27 Jul 2017)
\emph{Local large deviations and the strong renewal theorem},
SPA 2017 Conference, ``Random Walks'' Invited Session, Moscow (RU).

\item (5 Jun 2017)
\emph{Marginally relevant polymer models in the critical window},
Conference ``Statistical Mechanics, random planar geometry and interacting random walks'',
University of Lyon~1 (F).

\item (8 May 2017)
\emph{Marginally relevant polymer models in the critical window},
Workshop on ``Large scale random structures'',
University of Roma Tre (I).

\item (12 Dec 2016)
\emph{Universality in marginally relevant disordered systems},
Workshop ``Guided Tour: Random Media'' for the 60th birthday of Frank den Hollander,
Eurandom, Eindhoven~(NL).

\item (14 Jun 2016)
\emph{Scaling and universality in Probability},
Mathematics Colloquium of the University of Luxembourg (L).

\item (10 Sep 2015)
\emph{A multilinear extension of the central limit theorem
and the universality phenomenon for disordered systems},
XX Congress of the Italian Mathematical Union, Siena (I).

\item (31 Aug 2015)
\emph{Universality in marginally relevant disordered systems},
Meeting on ``Scaling Limits in Models of Statistical Mechanics'',
Oberwolfach Center of Mathematical Research (D).

\item (5 May 2015)
\emph{Polynomial chaos and scaling limits of disordered systems},
Workshop on Stochastic Processes in Random Media,  Institute for Mathematical Sciences,
National University of Singapore.

\item (28 Jul 2014)
\emph{The continuum disordered pinning model},
SPA 2014 Conference, ``Random Polymers'' Invited Session, Buenos Aires (AR).

\item (6 Jun 2014)
\emph{Polynomial chaos and scaling limits of disordered systems},
Statistical Mechanics Conference, University of Nantes (F).

\item (27 Apr 2014)
\emph{Polynomial chaos and scaling limits of disordered systems},
Mini-Workshop at NYU Abu Dhabi (UAE).

\item (13 Mar 2014)
\emph{Scaling and universality in Probability},
General Colloquium, Institute of Mathematics,
University of Leiden (NL).

\item (12 Sep 2013)
\emph{Scaling limits and universality for random pinning models},
15th Italian Meeting on Hyperbolic Equations,
University of Milano-Bicocca (I).

\item (9 Aug 2013)
\emph{Scaling limits and universality for random pinning models},
Workshop ``Universality and Scaling Limits in Probability and Statistical Mechanics'',
Hokkaido University, Sapporo (JP).

\item (21 Mar 2013)
\emph{Scaling limits and universality for random pinning models},
Workshop ``Analysis and Stochastics in Complex Physical Systems'', University of Leipzig (D).

%\item (10-12 Jan 2013)
%\emph{Random Polymers and Localization Strategies} [mini-course],
%School of ``Random Polymers'', Eurandom, Eindhoven~(NL).
%
%\item (14-18 May 2012)
%\emph{Random Polymers and Localization Strategies} [mini-course],
%Worshop ``Random Polymers and Related Topics'', Institute for Mathematical Sciences,
%National University of Singapore.
%
%\item (6-10 Sep 2011)
%\emph{The strange behavior of a random walk} [mini-course],
%Mathematics Summer School ``Alfa Class'' for top undergraduate students
%by ``Progetto Diderot'' -- Fondazione CRT, Solonghello (AL), Italy.

\item (15 Feb 2011)
\emph{The weak coupling limit of disordered copolymer models},
Workshop on Interacting Processes in Random Environments,
Fields Instutute, Toronto (CDN).

\item (16 Oct 2010)
\emph{The weak coupling limit of disordered copolymer models},
Workshop ``Probabilistic Methods in Statistical Physics''
on the occasion of Erwin Bolthausen's
65th birthday, Technische Universit\"at Berlin (D).

%\item (2-7 Aug 2010)
%\emph{Random Polymers} 
%[tutorials for the course given by Frank den Hollander;
%in collaboration with Nicolas P\'etr\'elis],
%XIV Brazilian School of Probability and
%Clay Mathematics Institute 2010 Summer School
%``Probability and Statistical Physics in Two and more Dimensions'',
%B\'uzios -- Rio de Janeiro (BR).

\item (7 Jun 2010)
\emph{Scaling and multiscaling in financial indexes: a simple model},
Workshop ``Statistical Mechanics and Random Media'',
University of Nantes~(F).

\item (11 Jun 2008)
\emph{Pinning and wetting transition for
(1+1)--dimensional fields with Laplacian interaction},
Workshop on Gradient Models and Elasticity, University of Warwick (UK).

\item (6 Mar 2008)
\emph{The quenched critical point of a diluted disordered polymer model},
GREFI-MEFI 2008 Workshop, CIRM, Marseille (F).

\item (26 Sep 2007)
\emph{Polymer models and random walks},
XVIII Congress of the Italian Mathematical Union, Bari (I).

\item (22 Jun 2007)
\emph{On the phase diagram of random copolymers at selective interfaces},
Workshop ``Random Polymer Models'',
Eurandom, Eindhoven~(NL).

\item (21 Feb 2007)
\emph{Pinning and wetting models with Laplacian interaction in (1+1)--di\-men\-sion},
Workshop ``Polymer Models and Related Topics'',
Laboratoire J.A. Dieudonn\'e, University of Nice `Sophia Antipolis'~(F).

\item (4 Sep 2006)
\emph{Pinning models with Laplacian interactions in (1+1)--dimension},
Meeting on ``Spatial Random Processes and Statistical Mechanics'',
Oberwolfach Center of Mathematical Research (D).

\item (6 Jun 2006)
\emph{A renewal theory approach to weakly inhomogeneous polymer models},
Workshop ``Hydrodynamic Limits and Particle Systems'',
\emph{Ennio De Giorgi} Center of Mathematical Research in Pisa (I).
\end{itemize}


%\pagebreak

\medskip
{\large\sf \bfseries Talks at Universities}
\smallskip

\begin{itemize}
\item (28 Jan 2025)
\emph{General Noise Sensitivity and Critical 2D Directed Polymers},
University of Grenoble (F).

\item (21 Nov 2024)
\emph{The 2D Stochastic Heat Equation and related critical models},
SISSA, Trieste (I).

\item (12 Jun 2023)
\emph{The critical 2d Stochastic Heat Flow},
University of Oxford (UK).

\item (1 Mar 2023)
\emph{The critical 2d Stochastic Heat Flow},
University of Zurich (CH).

\item (19 Mag 2022)
\emph{The critical 2d Stochastic Heat Flow},
GSSI, L'Aquila (I).

\item (25 Ott 2021)
\emph{Hairer's Reconstruction Theorem without Regularity Structures},
organized by TU Delft (NL) [online talk]

\item (15 Dec 2020)
\emph{On the two-dimensional KPZ and Stochastic Heat Equation},
Vienna Probability Seminar (A) [online talk]
%, due to the Covid-19 emergency]

\item (11 Nov 2020)
\emph{On the two-dimensional KPZ and Stochastic Heat Equation},
organized by University College Dublin (IE) [online talk]
%, due to the Covid-19 emergency]

\item (11 Jun 2020)
\emph{Hairer's Reconstruction Theorem without Regularity Structures},
organized by TU~Berlin (D) [online talk]
%, due to the Covid-19 emergency]

\item (27 Jan 2020)
\emph{On the two-dimensional KPZ and Stochastic Heat Equation},
Sapienza Universit\`a di Roma (I).

\item (27 Sep 2018)
\emph{Local large deviations and the strong renewal theorem},
DEC-Statistics Seminar, Bocconi University, Milan (I).

\item (6 Mar 2018)
\emph{Moment asymptotics for 2d directed polymer and stochastic 
heat equation in the critical window},
Stochastic Analysis Seminar, Imperial College, London (UK).

\item (9 Feb 2018)
\emph{Pinning model, universality and rough paths},
Rhein-Main Kolloquium Stochastik, Technische Universit\"at Darmstadt (D).

\item (23 May 2017)
\emph{Marginally relevant polymer models in the critical window},
University of Grenoble (F).

\item (15 Jun 2016)
\emph{Universality in marginally relevant disordered systems},
University of Luxembourg (L).

\item (2 Jun 2016)
\emph{Universality in marginally relevant disordered systems},
University of Paris Diderot (F).

\item (19 Nov 2015)
\emph{Multi-linear central limit theorems and scaling limits of disordered systems},
Vienna Seminar in Mathematical Finance and Probability (A).

\item (19 Mar 2015)
\emph{Polynomial chaos and scaling limits of disordered systems},
Probability Seminar, ENS Lyon (F).

\item (11 Oct 2013)
\emph{Polynomial chaos and scaling limits of disordered systems},
University of Padova (I).

\item (12 Jul 2013)
\emph{Scaling limits and universality for random pinning models},
Rhein-Main Kolloquium Stochastik, University of Mainz (D).

\item (13 Jun 2013)
\emph{Scaling limits and universality for random pinning models},
Most Informal Probability Seminar, University of Leiden (NL).

\item (10 Jun 2013)
\emph{Scaling limits and universality for random pinning models},
University of Angers (F).

\item (27 Jul 2012)
\emph{Scaling and multiscaling in financial series: a simple model},
Department of Statistics and Quantitative Methods,
University of Milano-Bicocca (I).

\item (10 Jul 2012)
\emph{A random copolymer near a selective interface},
University of Roma Sapienza (I).

\item (3 Apr 2012)
\emph{Bootstrap percolation on Galton Watson trees},
Most Informal Probability Seminar, University of Leiden (NL).

\item (12 Mar 2012)
\emph{Scaling and multiscaling in financial series: a simple model},
University of Modena and Reggio Emilia (I).

\item (23 Sep 2011)
\emph{Scaling and multiscaling in financial indexes: a simple model},
University of Rome Tor Vergata (I).

\item (16 Dec 2010)
\emph{A polymer in a multi-interface medium},
Oberseminar Stochastics,
University of Bonn (D).

\item (2 Nov 2010)
\emph{Scaling and multiscaling in financial indexes: a simple model},
University of Milano-Bicocca (I).

\item (10 Jun 2010)
\emph{The weak coupling limit of disordered copolymer models},
University of Warwick~(UK).

\item (20 May 2010)
\emph{Scaling and multiscaling in financial indexes: a simple model},
University of Padova~(I).

\item (1 Feb 2010)
\emph{Scaling and multiscaling in financial indexes: a simple model},
University of Pavia~(I).

\item (8 Dec 2009)
\emph{A polymer in a multi-interface medium},
S\'eminaire de Probabilit\'es,
Laboratoire de Probabilit\'es et Mod\`eles Al\'eatoires,
Universities of Paris 6 and Paris 7 (F).

\item (5 Nov 2009)
\emph{Large scale behavior of semiflexible heteropolymers},
University of Nantes (F).

\item (21 Jul 2009)
\emph{A polymer in a multi-interface medium},
University of Roma 3 (I).

\item (12 Nov 2008)
\emph{A polymer in a multi-interface medium},
Berliner Kolloquium Wahr\-schein\-lich\-keits\-theo\-rie
(IRTG Seminar), Humboldt University in Berlin (D).

\item (19 Jun 2008)
\emph{Pinning and wetting transition for
(1+1)--dimensional fields with Laplacian interaction},
S\'eminaire de Probabilit\'es, ENS Lyon (F).

\item (30 Apr 2008)
\emph{Pinning and wetting transition for
(1+1)--dimensional fields with Laplacian interaction},
Seminar on Stochastic Processes, University of Z\"urich (CH).

\item (23 Oct 2007)
\emph{The quenched critical point of a diluted disordered polymer model},
Random Spatial Structures Seminar, Eurandom, Eindhoven (NL).

\item (17 Jul 2007)
\emph{The quenched critical point of a diluted disordered polymer model},
St.~Flour Summer School of Probability (F).

\item (24 Jan 2007)
\emph{Free energy lower bounds for random copolymers at selective interfaces},
Technical University of Berlin~(D).

\item (13 Jul 2006)
\emph{Pinning models with Laplacian interactions in (1+1)--dimension},
Random Spatial Structures Seminar, Eurandom, Eindhoven (NL).

\item (17 Mar 2006)
\emph{A renewal theory approach to periodically inhomogeneous polymer models},
Seminaire de Probabilit\'es et Statistique, Centre de Math\'ematiques et Informatique,
University of Provence, Marseille (F).

\item (21 Dec 2005)
\emph{A local limit theorem and an invariance principle for random walks conditioned
to stay positive},
Seminar on Stochastic Processes, ETH Z\"urich (CH).

\item (16 Dec 2005)
\emph{A renewal theory approach to periodically inhomogeneous polymer models},
Berlin-Leipzig Seminar, Technical University of Berlin (D).

\item (19 Jul 2005)
\emph{A renewal theory approach to periodically inhomogeneous polymer models},
St.~Flour Summer School of Probability (F).

\item (27 May 2005)
\emph{Random copolymers at selective interfaces},
University of Milano-Bicocca (I).

\item (2 Jun 2004)
\emph{A local limit theorem for random walks conditioned to stay positive},
Rencontres de Probabilit\'es,
University of Rouen (F).
\end{itemize}

%\newpage

\medskip
{\large\sf \bfseries Didactic Talks}
\smallskip

\begin{itemize}
\item (20 Mar 2025)
\emph{Predictions, Gambling, and Popular Myths},
Collegio Ghislieri, Pavia (I).

\item (17 Jun 2022) \emph{Mathematics and chance: probability theory},
lecture for an audience of high school students,
Summer School ``An Introduction to College Mathematics'',
University of Milano-Bicocca (I).

\item (4 Sep 2019) \emph{Mathematics and chance},
talk for an audience of high school students,
Summer School ``La Matematica Oggi'',
San Pellegrino Terme, BG (I).

\item (12 Mar 2015) \emph{Mathematics in the university},
talk for an audience of high school students, Open Day
``Privavera in Bicocca 2015''.

\item (14 Mar 2013) \emph{Research in mathematics},
talk for an audience of high school students, Open Day
``Privavera in Bicocca 2013''.

\item (5 Nov 2008) \emph{The Banach-Tarski Paradox},
Technische Universit\"at Berlin (D).

\item (29 June 2006) \emph{What is\ldots the Banach-Tarski Paradox?},
Z\"urich Graduate Colloquium (CH).
\end{itemize}


%\newpage

\section{Teaching Experience}

\nopagebreak

%I gave undergraduate courses and recitations in several
%universities (Milano-Bicocca, Padova, Zurich, Politecnico di Milano).
%I also gave more advanced courses for Ph.D. programs, schools
%and workshops.

%\newpage

\medskip
{\large\sf \bfseries Research courses in schools and workshops}
\smallskip

\begin{itemize}
\item (15 Oct - 22 Nov 2024)
\emph{The critical 2d Stochastic Heat Flow and related models} 
[3~x~(2~x~1h) online],
in collaboration with Rongfeng Sun and Nikos Zygouras,
\href{https://sites.google.com/view/snuprob/seminar/intensive-lecture-series}{``Intensive Lecture Series''},
Seoul National University (KR).

\item (14-20 May 2024)
\emph{The critical 2d Stochastic Heat Flow} [3~x~2h],
in collaboration with Rongfeng Sun and Nikos Zygouras,
\href{https://bicmr.pku.edu.cn/content/show/17-3296.html}{``Spring School on Critical Singular SPDEs''},
Beijing International Center for Mathematical Research (BICMR),
Peking University (CN).

\item (11-15 Sep 2023)
\emph{The critical 2d Stochastic Heat Flow} [3~x~1.5h],
in collaboration with Rongfeng Sun and Nikos Zygouras,
C.I.M.E. Summer School ``Statistical Mechanics and Stochastic PDEs'',
Cetraro (CS), Italy.

\item (19-22 Mar 2021)
\emph{Gaussian Limits for 2d Directed Polymers, KPZ and SHE} [3~x~(2~x~1.5h) online],
in collaboration with Rongfeng Sun and Nikos Zygouras,
Berlin-Oxford IRTG 
%[course given online, due to the Covid-19 emergency].

\item (10-11 Dec 2018)
\emph{On the two-dimensional KPZ and Stochastic Heat Equation 
via directed polymers} [2~x~1.5h],
Conference
``State of research: statistical mechanics'' of the
French Mathematical Society, %(Soci\'et\'e Math\'ematique de France),
Institut Henri Poincar\'e, Paris (F).

\item (2 Jun 2016)
\emph{Polynomial chaos and scaling limits of disordered systems} [3h],
%[corso ($5 \times 1.5$ ore)],
Working group on ``Statistical mechanics and particle systems'',
University of Paris Diderot (F).

\item (7 - 11 Mar 2016)
\emph{Polynomial chaos and scaling limits of disordered systems}
[3~x~1.5h],
Workshop YEP XIII, Eurandom, TU Eindhoven (NL).

\item (28 Sep - 2 Oct 2015)
\emph{Polynomial chaos and scaling limits of disordered systems}
[5~x~1.5h],
Berlin-Potsdam Summer School 2015, Levico Terme (I).

\item (10-12 Jan 2013)
\emph{Random Polymers and Localization Strategies} [3~x~2h],
School of ``Random Polymers'', Eurandom, Eindhoven~(NL).

\item (14-18 May 2012)
\emph{Random Polymers and Localization Strategies} [3~x~2h + 1h],
Worshop ``Random Polymers and Related Topics'', Institute for Mathematical Sciences,
National University of Singapore.

\item (6-10 Sep 2011)
\emph{The strange behavior of a random walk} [1.5h + 2h],
Mathematics Summer School ``Alfa Class'' for top undergraduate students
by ``Progetto Diderot'' -- Fondazione CRT, Solonghello (AL), Italy.

\item (2-7 Aug 2010)
\emph{Random Polymers} 
[5x1h tutorials, in collaboration with Nicolas P\'etr\'elis,
for the course given by Frank den Hollander],
XIV Brazilian School of Probability and
Clay Mathematics Institute 2010 Summer School
``Probability and Statistical Physics in Two and more Dimensions'',
B\'uzios -- Rio de Janeiro (BR).
\end{itemize}

%\newpage

\medskip
{\large\sf \bfseries Ph.D.\ Courses}
\smallskip



\begin{itemize}
\item (Fall 2024)
\textit{Stochastic Analysis and Applications},
Ph.D. in Mathematics, Universities of
Pavia and Milano-Bicocca [30h, with a seminar by Tal Orenshtein]

\item (Spring 2020)
\textit{Topics from the Gaussian World},
Ph.D. in Mathematics, Universities of
Pavia and Milano-Bicocca [30h, with Maurizia Rossi]

\item (Spring 2019)
\textit{An Introduction to Regularity Structures},
Ph.D. in Mathematics, Universities of
Pavia and Milano-Bicocca [30h]

\item (Spring 2017)
\textit{Rough Paths and Stochastic Differential Equations},
Ph.D. in Mathematics, Universities of Pavia and
Milano-Bicocca [30h, with Gianmario Tessitore]

\item (Spring 2014)
\textit{Random Graphs and Complex Networks},
Ph.D. in Mathematics, joint course ("interdottorato") for the Universities of
Milano, Milano-Bicocca, Pavia and Politecnico of Milano
[30h, with Federico Bassetti]

\item (Spring 2010) 
\textit{Random Graphs and Complex Networks},
Ph.D. in Mathematics, University of Padova
[20h, with Paolo Dai Pra]

\item (Spring 2009)
\emph{Poisson Point Processes and Applications},
Ph.D. in Mathematics, University of Padova
[10h]

\item (Fall 2006)
\emph{Polymer Models and Random Walks},
Ph.D. in Mathematics, University of Padova [10h]
\end{itemize}

%\newpage


\medskip
{\large\sf \bfseries Undergraduate Courses and Recitations}
\smallskip

\smallskip
\emph{At the University of Milano-Bicocca}

\begin{itemize}
\item (Spring 2025)
\textit{Probability and Statistics for Informatics} (course),
Bachelor's Degree in Informatics
[in collaboration with Federica Masiero and Maurizia Rossi]

\item (Fall 2024)
\textit{Stochastic Calculus and Finance} (course),
Master's Degree in Mathematics

\item (Fall 2024)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Spring 2024)
\textit{Probability and Statistics for Informatics} (course),
Bachelor's Degree in Informatics
[in collaboration with Federica Masiero and Maurizia Rossi]

\item (Fall 2023)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics

\item (Spring 2023)
\textit{Probability and Statistics for Informatics} (course),
Bachelor's Degree in Informatics
[in collaboration with Federica Masiero and Maurizia Rossi]

\item (Fall 2022)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics

\item (Spring 2022)
\textit{Probability and Statistics for Informatics} (course),
Bachelor's Degree in Informatics
[in collaboration with Federica Masiero and Maurizia Rossi]

\item (Fall 2021)
\textit{Probability Theory} (course + recitations),
Bachelor's Degree in Mathematics

\item (Spring 2021)
\textit{Probability and Statistics for Informatics} (course),
Bachelor's Degree in Informatics
[in collaboration with Federica Masiero and Maurizia Rossi]

\item (Spring 2021)
\textit{Stochastic Methods and Models} (course),
Master's Degree in Mathematics
[in collaboration with Maurizia Rossi]

\item (Fall 2020)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics

\item (Fall 2019)
\textit{Stochastic Methods for Finance} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2019)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics

\item (Spring 2019)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2018)
\textit{Stochastic Methods for Finance} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2018)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics

\item (Spring 2018)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2017)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics

\item (Spring 2017)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2016)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics

\item (Spring 2016)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2015)
\textit{Probability Theory} (course),
Bachelor's Degree in Mathematics

\item (Spring 2015)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2014)
\textit{Probability Theory} (course + recitations),
Bachelor's Degree in Mathematics

\item (Spring 2014)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2013)
\textit{Probability Theory} (course + recitations),
Bachelor's Degree in Mathematics

\item (Spring 2013)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

%\item (Spring 2013)
%\emph{Random Polymers and Localization Strategies} (mini-course),
%School of ``Random Polymers'', Eurandom, Eindhoven~(NL),
%10-12 Jan 2013

\item (Fall 2012)
\textit{Probability Theory} (course + recitations),
Bachelor's Degree in Mathematics

%\item (Spring 2012)
%\emph{Random Polymers and Localization Strategies} (mini-course),
%Worshop ``Random Polymers and Related Topics'', Institute for Mathematical Sciences,
%National University of Singapore, 14-18 May 2012

\item (Spring 2012)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Fall 2011)
\textit{Probability Theory} (course + recitations),
Bachelor's Degree in Mathematics

\item (Spring 2011)
\textit{Stochastic Processes} (course),
Master's Degree in Mathematics
[in collaboration with Gianmario Tessitore]

\item (Spring 2005)
\emph{Stochastic Processes} (recitations),
Master's Degree in Mathematics 
[teacher: Gianmario Tessitore]

\item (Spring 2004)
\emph{Stochastic Processes} (recitations),
Master's Degree in Mathematics 
[teacher: Daniela Bertacchi]

\item (Spring 2004)
\emph{Probability and Statistics} (recitations),
Bachelor's Degree in Mathematics 
[teacher: Daniela Bertacchi]
\end{itemize}

%\newpage

\smallskip
\emph{At the University of Padova}

\begin{itemize}
\item (Spring 2011)
\emph{Stochastic Calculus} (course),
Master's Degree in Mathematics
[in collaboration with David Barbato]

%\item (2-7 Aug 2010)
%Tutorials for the mini-course \emph{Random Polymers},
%XIV Brazilian School of Probability and
%Clay Mathematics Institute 2010 Summer School
%``Probability and Statistical Physics in Two and more Dimensions'',
%B\'uzios -- Rio de Janeiro (BR)
%[teacher: Frank den Hollander; in collaboration with Nicolas P\'etr\'elis]

\item (Spring 2010)
\emph{Statistics} (recitations),
Bachelor's Degree in Molecular Biology
[teacher: Paolo Dai Pra]

\item (Spring 2010)
\emph{Stochastic Calculus} (course),
Master's Degree in Mathematics

\item (Spring 2009)
\emph{Probability and Statistics} (recitations),
Bachelor's Degree in Mathematics
[teacher: Paolo Dai Pra]

\item (Spring 2009)
\emph{Stochastic Calculus} (course),
Master's Degree in Mathematics

\item (Spring 2008)
\emph{Probability Theory} (course),
Bachelor's Degree in Engineering, 
University of Padova (I) [in collaboration with Caterina Sartori]

\item (Spring 2008)
\emph{Probability and Statistics} (recitations),
Bachelor's Degree in Mathematics
[teacher: Paolo Dai Pra]

\item (Spring 2008)
\emph{Statistical Methods for Biology} (recitations),
Bachelor's Degree in Biology
[teacher: Paolo Dai Pra]

\item (Spring 2007)
\emph{Statistical Methods for Biology} (recitations),
Bachelor's Degree in Molecular Biology
[teacher: Paolo Dai Pra]

\item (Spring 2007)
\emph{Statistical Methods for Biology} (recitations),
Bachelor's Degree in Biology
[teacher: Paolo Dai Pra]
\end{itemize}

%\newpage

\smallskip
\emph{At the University of Zurich}


\begin{itemize}
\item (Spring 2006)
\emph{Linear Algebra II} (recitations),
Bachelor's Degree in Mathematics
[teacher: Erwin Bolthausen]

\item (Fall 2005)
\emph{Linear Algebra I} (recitations),
Bachelor's Degree in Mathematics
[teacher: Erwin Bolthausen]
\end{itemize}

%\newpage

\smallskip
\emph{At Politecnico di Milano}

\begin{itemize}
\item (Spring 2003)
\emph{Probability and Statistics} (on-line recitations),
Bachelor's Degree in Engineering
[teacher: Elio Piazza]

\item (Spring 2003)
\emph{Probability and Statistics} (numerical laboratory),
Bachelor's Degree in Engineering [teacher: Elio Piazza]
\end{itemize}


\end{document}

